Tobacco Transition Module

### 2022-12-19 docsrc/documentation/notebooks/household_income.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "Household_Income"
output: html_document
date: "2022-12-16"
bibliography: references.bib  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

@@

>>>>

---
title: "Household Income"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib"
---

@@

Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

  What methods are used? Justification due to output data type. explanation of model output.

@@

  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen

@@

  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.

```{r income_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/hh_income_2018_2019.rds")
```

## References

### 2022-12-19 docsrc/documentation/notebooks/housing.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "Household Income"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib"
---

# Household Income

@@

```{r income_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/hh_income_2018_2019.rds")
```

>>>>

---
title: "Housing"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Housing Quality

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```

### 2022-12-19 docsrc/documentation/notebooks/labour.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "Housing"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Housing Quality

Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```

>>>>

---
title: "Labour"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Labour

Introductory fluff. Why do we need this module? test reference [@1987:nelson].

@@

```{r housing_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

### 2022-12-19 docsrc/documentation/notebooks/loneliness.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "Labour"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Labour

@@

```{r housing_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

>>>>

---
title: "Loneliness"
output: html_document
bibliography: 
  - "refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging. Make sure to switch back when done..
---

# Loneliness

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

### 2022-12-19 docsrc/documentation/notebooks/mental_well_being.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "Housing"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Housing Quality

Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```

>>>>

---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "refs.bib" # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Mental Well-Being

Introductory fluff. Why do we need this module? test reference [@1987:nelson].

@@

```{r housing_output, echo=FALSE}
options(width=120)
ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

### 2022-12-19 docsrc/documentation/notebooks/module_notebook_template.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "Labour"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Labour

@@

```{r housing_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

>>>>

---
title: "XXXX"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# XXXX

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("PATH_TO_TEST_MODEL_DATA") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

### 2022-12-19 docsrc/documentation/notebooks/neighbourhood.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "XXXX"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# XXXX

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("PATH_TO_TEST_MODEL_DATA") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

>>>>

---
title: "Neighbourhood"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Neighbourhood

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

### 2022-12-19 docsrc/documentation/notebooks/tobacco.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

---
title: "tobacco"
output: html_document
date: "2022-12-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "Tobacco Transition Module"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Tobacco

Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

  What methods are used? Justification due to output data type. explanation of model output.

## Data

  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen

## Results

  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
```

## References
